---
title: "Introduction to Web Scraping and Data Management for Social Scientists"
subtitle: "Essex Summer School in Social Science Data Analysis 2026"
author: "[Dr Johannes B. Gruber](https://www.johannesbgruber.eu/)"
format:
  html:
    toc: false
execute:
  echo: false
  freeze: false
---

## Welcome to the Course

This is the course material for the Essex Summer School in Social Science Data Analysis course [2H Introduction to Web Scraping and Data Management for Social Scientists](https://essexsummerschool.com/course/ess-2026-course-list/2h/), Monday 20 July–Friday 31 July 2026.

The course provides an introduction to the automated collection of data from the internet, as well as methods for efficient and safe data management.
The first week covers different modes of storing data for individual researchers and research teams, and the theory and good practices behind them.
The second week focuses on methods for collecting different kinds of data from the internet through various means.

## Schedule

Slides are uploaded here as the course progresses.

```{r}
#| message: false
library(tibble)

link_md <- function(paths, labels) {
  ifelse(
    file.exists(file.path("docs", paste0(paths, ".html"))),
    sprintf("[%s](%s.html)", labels, paths),
    NA_character_
  )
}

fmt_links <- function(paths_str) {
  if (is.na(paths_str)) return("–")
  paths <- strsplit(paths_str, ";")[[1]]
  labels <- if (length(paths) > 1) paste("Part", seq_along(paths)) else "Slides"
  links <- link_md(paths, labels)
  links <- links[!is.na(links)]
  if (length(links) == 0) "*not yet available*" else paste(links, collapse = " / ")
}

sessions <- tribble(
  ~Day, ~Date, ~Session, ~slides, ~solutions,
  1, "Mon, 20 July", "Introduction", "01_Introduction/01_Introduction", "01_Introduction/01_solutions",
  2, "Tue, 21 July", "Data Structures and Wrangling", "02_Data_Structures_Wrangling/02_Data_Structures_Wrangling", "02_Data_Structures_Wrangling/02_solutions",
  3, "Wed, 22 July", "Working with Files", "03_Working_with_Files/03_Working_with_Files", "03_Working_with_Files/03_solutions",
  4, "Thu, 23 July", "Linking and Joining Data & SQL", "04_Linking_and_joining_data_SQL/04_Linking_and_joining_data_SQL", "04_Linking_and_joining_data_SQL/04_solutions",
  5, "Fri, 24 July", "Scaling, Reporting and Database Software", "05_Scaling_Reporting_and_Database_Software/05_Scaling_Reporting_and_Database_Software", "05_Scaling_Reporting_and_Database_Software/05_solutions",
  6, "Mon, 27 July", "Introduction to the Web", "06_Introduction_to_the_Web/06_Introduction_to_the_Web", "06_Introduction_to_the_Web/06_solutions",
  7, "Tue, 28 July", "Static Web Pages", "07_Static_Web_Pages/07_Static_Web_Pages", "07_Static_Web_Pages/07_solutions",
  8, "Wed, 29 July", "Application Programming Interfaces (APIs)", "08_APIs/08_APIs", "08_APIs/08_solutions",
  9, "Thu, 30 July", "Interactive Web Pages", "09_Interactive_Web_Pages/09_Interactive_Web_Pages_1;09_Interactive_Web_Pages/09_Interactive_Web_Pages_2", NA,
  10, "Fri, 31 July", "Building a Reproducible Research Project", "10_Conclusion/10_Conclusion", NA
)

sessions$Materials <- vapply(sessions$slides, fmt_links, character(1))
sessions$Exercises <- vapply(sessions$solutions, fmt_links, character(1))
sessions$Exercises <- sub("Slides", "Exercises", sessions$Exercises)

knitr::kable(sessions[, c("Day", "Date", "Session", "Materials", "Exercises")])
```

## Required Software

You should have several software applications installed before the start of the course:

- [R](https://cran.r-project.org/) (version 4.1.0+)
- An IDE, preferably [RStudio Desktop](https://posit.co/download/rstudio-desktop/), but you can also use [VSCodium](https://vscodium.com/) or [VS Code](https://code.visualstudio.com/download) or [Positron](https://github.com/posit-dev/positron)
- [Quarto](https://quarto.org/docs/get-started/)

## Download Course Materials

Clone the repository using RStudio:

1. Create a new project (top left corner)
2. Select "Version Control" → "Git"
3. Use URL: `https://github.com/JBGruber/ess-web-scraping-data-management.git`

## Install Required Packages

After cloning, you can install all required R packages with:

```{r}
#| echo: true
#| eval: false
if (!requireNamespace("rlang", quietly = TRUE)) {
  install.packages("rlang", dependencies = TRUE)
}
rlang::check_installed("remotes")
if (!requireNamespace("jbgtemplates", quietly = TRUE)) {
  remotes::install_github("JBGruber/jbgtemplates")
}
jbgtemplates::install_deps(gh_packages = c(
  "JBGruber/paperboy",
  "JBGruber/playwrightr",
  "ccs-amsterdam/amcat4r"
))
```

---

*Course by [Dr Johannes B. Gruber](https://www.johannesbgruber.eu/) • [GitHub Repository](https://github.com/JBGruber/ess-web-scraping-data-management)*
