---
title: "solutions session 2"
format: html
---

## Exercises 3

1. replace all whitespace characters in the country columns of `country_df` with underscores (`_`)
2. remove all punctuation from the `data_input` vector

```{r}
data_input <- "
Albania is a country with 2.8 million inhabitants, its capital is Tirana, and it was founded on 28 November 1912.
Andorra is a country with 77,000 inhabitants, its capital is Andorra la Vella, and it was founded on 8 September 1278.
Austria is a country with 8.9 million inhabitants, its capital is Vienna, and it was founded on 12 November 1918.
Belarus is a country with 9.5 million inhabitants, its capital is Minsk, and it was founded on 25 August 1991.
Belgium is a country with 11.5 million inhabitants, its capital is Brussels, and it was founded on 4 October 1830.
Bosnia and Herzegovina is a country with 3.3 million inhabitants, its capital is Sarajevo, and it was founded on 1 March 1992.
Bulgaria is a country with 6.9 million inhabitants, its capital is Sofia, and it was founded on 22 September 1908.
Croatia is a country with 4 million inhabitants, its capital is Zagreb, and it was founded on 25 June 1991.
Cyprus is a country with 1.2 million inhabitants, its capital is Nicosia, and it was founded on 16 August 1960.
Czech Republic is a country with 10.7 million inhabitants, its capital is Prague, and it was founded on 1 January 1993.
Denmark is a country with 5.8 million inhabitants, its capital is Copenhagen, and it was founded on 5 June 1849.
Estonia is a country with 1.3 million inhabitants, its capital is Tallinn, and it was founded on 20 August 1991.
Finland is a country with 5.5 million inhabitants, its capital is Helsinki, and it was founded on 6 December 1917.
France is a country with 67 million inhabitants, its capital is Paris, and it was founded on 22 September 1792.
Germany is a country with 83 million inhabitants, its capital is Berlin, and it was founded on 3 October 1990.
Greece is a country with 10.4 million inhabitants, its capital is Athens, and it was founded on 25 March 1821.
Hungary is a country with 9.6 million inhabitants, its capital is Budapest, and it was founded on 23 October 1989.
Iceland is a country with 366,000 inhabitants, its capital is Reykjavik, and it was founded on 17 June 1944.
Ireland is a country with 5 million inhabitants, its capital is Dublin, and it was founded on 6 December 1922.
Italy is a country with 60 million inhabitants, its capital is Rome, and it was founded on 17 March 1861.
Kosovo is a country with 1.8 million inhabitants, its capital is Pristina, and it was founded on 17 February 2008.
Latvia is a country with 1.9 million inhabitants, its capital is Riga, and it was founded on 18 November 1918.
Liechtenstein is a country with 39,000 inhabitants, its capital is Vaduz, and it was founded on 23 January 1719.
Lithuania is a country with 2.8 million inhabitants, its capital is Vilnius, and it was founded on 11 March 1990.
Luxembourg is a country with 634,000 inhabitants, its capital is Luxembourg City, and it was founded on 9 June 1815.
Malta is a country with 514,000 inhabitants, its capital is Valletta, and it was founded on 21 September 1964.
Moldova is a country with 2.6 million inhabitants, its capital is Chișinău, and it was founded on 27 August 1991.
Monaco is a country with 39,000 inhabitants, its capital is Monaco, and it was founded on 8 January 1297.
Montenegro is a country with 622,000 inhabitants, its capital is Podgorica, and it was founded on 3 June 2006.
Netherlands is a country with 17.4 million inhabitants, its capital is Amsterdam, and it was founded on 26 July 1581.
North Macedonia is a country with 2.1 million inhabitants, its capital is Skopje, and it was founded on 8 September 1991.
Norway is a country with 5.4 million inhabitants, its capital is Oslo, and it was founded on 7 June 1905.
Poland is a country with 38 million inhabitants, its capital is Warsaw, and it was founded on 11 November 1918.
Portugal is a country with 10.3 million inhabitants, its capital is Lisbon, and it was founded on 5 October 1143.
Romania is a country with 19 million inhabitants, its capital is Bucharest, and it was founded on 1 December 1918.
Russia is a country with 144 million inhabitants, its capital is Moscow, and it was founded on 12 June 1990.
San Marino is a country with 34,000 inhabitants, its capital is San Marino, and it was founded on 3 September 301.
Serbia is a country with 6.7 million inhabitants, its capital is Belgrade, and it was founded on 5 June 2006.
Slovakia is a country with 5.4 million inhabitants, its capital is Bratislava, and it was founded on 1 January 1993.
Slovenia is a country with 2.1 million inhabitants, its capital is Ljubljana, and it was founded on 25 June 1991.
Spain is a country with 47 million inhabitants, its capital is Madrid, and it was founded on 6 December 1978.
Sweden is a country with 10.4 million inhabitants, its capital is Stockholm, and it was founded on 6 June 1523.
Switzerland is a country with 8.3 million inhabitants, its capital is Bern, and it was founded on 12 September 1848.
Ukraine is a country with 41 million inhabitants, its capital is Kyiv, and it was founded on 24 August 1991.
United Kingdom is a country with 67 million inhabitants, its capital is London, and it was founded on 1 January 1801.
Vatican City is a country with 825 inhabitants, its capital is Vatican City, and it was founded on 11 February 1929.
"
```

```{r}
library(stringr)
```

3. Extract the date from the string and turn it into a proper date vector:

```{r}
string <- "Military defeats following the outbreak of the French Revolutionary Wars resulted in the insurrection of 10 August 1792. The monarchy was abolished and replaced by the French First Republic one month later."
```

4. Check which of the lines in `data_input` have the word "million" (hint: you need to split the string into a vector with `str_split()` first)
5. Now save a subset of the lines into a new object
6. From the following vector, I want you to write code that identifies the URLs from the German Wikipedia that do *not* use the secure Hypertext Transfer Protocol (HTTPS):

```{r}
vec <- c(
  "https://en.wikipedia.org/wiki/France",
  "https://en.wikipedia.org/wiki/Germany",
  "https://de.wikipedia.org/wiki/Deutschland",
  "http://de.wikipedia.org/wiki/Frankreich",
  "https://de.wikipedia.org/wiki/Belgien",
  "https://de.wikipedia.org/wiki/Bulgarien",
  "http://de.wikipedia.org/wiki/K%C3%B6nigreich_D%C3%A4nemark",
  "https://de.wikipedia.org/wiki/Slowenien",
  "https://de.wikipedia.org/wiki/Rum%C3%A4nien"
)
```

## Exercises 4

1. From the `airports` table in the `nycflights13` package, access all airports that are in the Los Angeles time zone:

```{r}
airports <- nycflights13::airports
```

2. Access the `faa` of the airport at latitude 40.87522 and longitude -74.28136
3. The Las Vegas International Aiport (LAS) has been renamed since the dataset was created. Update the name to "Harry Reid International"
4. Delete all aiports that have `NA` as their timezone

## Exercises 5

1. Look at the table `billboard` that is included in `tidyr`. What is not tidy about it?

```{r}
billboard
```

2. Tidy the data
3. The new table contains many missing values (`NA`s) explain why and if you should delete them
4. Independently from whether it is the right thing to do or now: delete the `NA`s
4. Why does this code fail?

```{r}
#| error: true
table4a |>
  pivot_longer(c(1999, 2000), names_to = "year", values_to = "cases")
```

5. Make this into a tidy table

```{r}
preg <- tribble(
  ~pregnant , ~male , ~female ,
  "yes"     , NA    ,      10 ,
  "no"      ,    20 ,      12
)
```

## Exercises 6

1. The object below is a nested list with Game of Thrones characters. Tidy the data into a data.frame that contains at least name, gender, culture and birthday of each character

```{r}
got_characters <- repurrrsive::got_chars
```

2. From the `got_characters` object, also extract in which season(s) they appear, so that the data frame contains one row per season appearance (and still the same character information as above) 

3. Sometimes, it makes sense to keep nested information around for later. The `got_characters` object contains aliases for the characters. Store them along the character name in a nested format, so that each row looks like this:

```{r}
tibble(
  name = "Theon Greyjoy",
  aliases = list(c(
    "Prince of Fools",
    "Theon Turncloak",
    "Reek",
    "Theon Kinslaye"
  ))
)
```

4. The object below contains someone's music collection. Create a tidy table of the artist this person listens to:

```{r}
music_collection <- repurrrsive::discog
```

5. Now add the title of the songs to the artists table